
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.2in,top=0.3in,right=0.2in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ben Millar} % Your name
\address{www.linkedin.com/in/benmarkmillar} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{benmarkmillar@gmail.com} % Your phone number and email

\begin{document}

\begin{rSection}{About}
I am a First Class MPhys graduate from the University of St Andrews who has successfully managed a demanding course load across multiple disciplines, showcasing exceptional time management and intellectual versatility. I thrive in environments that encourage innovation, critical thinking, and collaborative problem-solving. With significant research and practical experience in quantitative analysis, my goal is to leverage these skills in finance, data science, and related fields.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

\begin{rSubsection}{University of St. Andrews}{2018-2024}{}
\\ {\bf MPhys (Hons), Mathematics and Theoretical Physics} {\bf First Class}

\item{Master's courses in Quantum Field Theory, Stochastic Dynamics, Calculus of Variations, Spatial Models and Pattern Formation, Mathematical Oncology.}

\item{Honours courses in Financial Mathematics, Functional Analysis, Group Theory, Linear Algebra, Real \& Complex Analysis, Fluid Dynamics, Special Relativity \& Classical Fields, Condensed Matter Physics, Lagrangian \& Hamiltonian Dynamics, Computational Physics.}

\item{Over-credited to join both the pure mathematics and applied mathematics honours track, in addition to doing a joint degree with theoretical physics.} 
\item{\textit{Dean's List for Academic Excellence.}}
% \item{PLANCKS national theoretical physics competition finalist, IoP (2020, 2021)}
% Additionally selected for the following programmes:  
% - Entrepreneurship Centre Faststart Web Development (2022-23)  
% - Philosophy of Science, University of Oxford (2022)  
% - London Mathematical Society Summer School (2021)  
% - Particle Physics, University of Göttingen (2021)  
% - Data Science Bootcamp Wolfram (2020)

\setlength{\leftskip}{0.5cm}
\item{\bf Activities \& Societies:} Effective Altruism, Engineering Society and Physics Society (Careers \& Professional Outreach Officer), Entrepreneurship Centre Faststart Web Development Programme. %London Mathematical Society Summer School.

\end{rSubsection}

\setlength{\leftskip}{0cm}

\begin{rSubsection}{George Heriot's School}{2012-2018}{}

\item{\textbf{Scottish Advanced Higher (2018): Mathematics, Physics, Mechanics - All A1}}
\item{Scottish Higher (2017): Mathematics (A1), Physics (A), Human Biology (A1), Philosophy (A1), English (A1)
\\ Scottish National 5 (2016): Mathematics, Physics, Chemistry, Biology, English, Philosophy - All A1. Modern Studies, French - A}
\item{Awards: Senior Mathematical Challenge Gold Award, United Kingdom Mathematics Trust (2016, 2017). CREST Gold Award, British Science Association (2018). Dux in Mathematics (2017). Physics Prize (2017). Philosophy Prize (2015, 2016). English Prize (2016).
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Python, Wolfram Language (Mathematica), Javascript, SQL, Maple\\
More Languages & \LaTeX , HTML, CSS \\
Skills & Data Science, Web Development \\
\end{tabular}

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{Quant Analyst}{Sep 2023 - Sep 2024}{Mercury Capital Management}

    \item{Mercury Capital Management is a Multi-Asset research focused student fund specialising in small-cap companies.}
    \item{Worked in the Quant team identifying alpha generating strategies, building a technical understanding of these, implementing and backtesting. Communicated findings to the rest of the fund.}
    \item{Completed the Algorithmic Trading A-Z Course (QuantConnect).}
    
\end{rSubsection}
% \newpage
\begin{rSubsection}{Theoretical Physics Researcher}{Feb - Apr 2024}{School of Physics and Astronomy, University of St. Andrews}

    \item {Masters thesis titled `Phase Diagram of Mixed Spin Chains', investigating the balance of ordering and thermal fluctuations in low dimensional spin systems.}
    \item{Efficiently calculated the partition function of mixed spin systems using the transfer matrix method. Modelled magnetic coupling between layers of Sr4Ru3O10, comparing response of longitudinally and transversely applied magnetic fields. Constructed a phase diagram for ferromagnetic, antiferromagnetic and paramagnetic orderings.}
    \item {Generalised algorithm to generate and diagonalise transfer matrix for any choice of Hamiltonian and spin configuration space. Quantified the influence of external and internal system parameter variations. Produced magnetic susceptibility and heat capacity response function plots, as well as for magnetisation. }
    \item {Successful working under pressure, completing project in 60\% of expected time frame.}

\end{rSubsection}

\begin{rSubsection}{Mathematical Physics Researcher}{May-Aug 2023}{Quantum Materials, University of St. Andrews}

\item{Research project investigating the representation theory of loop-U(1) groups as a basis for a rigorous theory of `strange metals', which exhibit behaviour not explained by Landau's Fermi liquid theory.}
\item{Associated with the Hooley Group in theoretical condensed matter physics and quantum materials.}
\item{Secured competitive funding through an SSC Award and Physics Trust Bursary.}
\end{rSubsection}

\begin{rSubsection}{Summer School Student in Theoretical Physics}{August 2022}{Utrecht University}

\item Advanced undergraduate courses including topics in general relativity, path integrals, and soft matter physics.
    
\end{rSubsection}

\begin{rSubsection}{Machine Learning and Photography Project}{May - Jun 2021}{University of St. Andrews}

\item{Built a machine learning model to classify and categorise the university’s photographic archives. The project was completed through St. Andrews’ Summer Team Enterprise Programme (STEP).}
\item{The project involved image extraction, data cleaning, multi-label classification, and sorting of 35,000+ photographs using the ML algorithm.}
\item{Presented findings to a non-technical audience, and making approach accessible. Conducted ethical analysis, addressing colonial past and sensitive language in archival descriptions.}
\item{Inter-disciplinary project with team members in art history and computer science backgrounds. Worked effectively online across continents and time zones.}
\end{rSubsection}

\begin{rSubsection}{Applied Mathematics Researcher, Solar and Magnetospheric Theory group}{Jul - Sep 2020}{School of Mathematics and Statistics, University of St. Andrews}

\item{Investigating the structure of solar coronal loops. Mathematical modelling of sun's outer atmosphere using Python. Implementing Runge-Kutta numerical methods to solve magnetohydrodynamic equations for anisotropic conduction of electrons in plasma.}    
\end{rSubsection}


\begin{rSubsection}{Intern (eLearning for Healthcare)}{May-Jul 2020}{NHS}


\item{Worked on Acute Medicine (ACUMEN) curriculum design, as well as Sexual Health and HIV-STI modules. (NHS England)}
\item{Developed skills in data analytics and visualisation.}
\item{Initiated website wire-framing and prototyping with Axure RP 9.}

\end{rSubsection}

\begin{rSubsection}{Physics and Mathematics Tutor}{2018-present}{}
    
\item I offer lessons to people studying Physics, Mathematics, and Further Mathematics up to and including Advanced Higher/A-level. Providing a relaxed, comfortable and inclusive environment for students that facilitates growth, nurturing interest and success. 
\end{rSubsection}

\begin{rSubsection}{Summer School Student in Theoretical Physics and Philosophy}{2017}{Harvard University} 

\item{High intensity undergraduate-level theoretical physics course (PHYS S-10). Final project `The Lorentz-Covariant Formulation of Classical Electromagnetism and the Maxwell Action' (Supervisor: Jacob Barandes). I also enrolled in a comparative literature class, COMP S-116: `Big Ideas, Great Thinkers'. I received an A grade for both courses.}
\end{rSubsection}


\end{rSection}



%----------------------------------------------------------------------------------------
% Courses
%----------------------------------------------------------------------------------------
% ------------------
%
% \begin{rSection}{Courses}
% \item {\bf Physics Courses:} Classical Mechanics, Oscillations, Thermal \& Statistical Physics, Electromagnetism,  Special Relativity, Quantum Mechanics, Astrophysics, Lagrangian \& Hamiltonian Dynamics, Computational Physics, and Physics, Astronomy \& Astrophysics Laboratory.
% \item {\bf Mathematics Courses:} Pure \& Applied Mathematics, Linear Mathematics, Abstract Algebra, Multivariate Calculus, Vector Calculus, Combinatorics \& Probability, Mathematical Modelling, Real \& Functional Analysis, Solar Physics.
% \
% \end{rSection}
%-------------

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\end{document}
